\Large Analyzing the Supreme Court Citation Network

### 2017-12-12 Tex/paper.tex
updating theory
New inferential results

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.319                                                 & -5.392                                                     & -5.243                                                     \\ \hline
Instar(2)               & 0.018                                                   & 0.017                                                      & 0.019                                                      \\ \hline
Outstar(2)              & 0.018                                                  & 0.016                                                      & 0.022                                                      \\ \hline
Mutual                  & 3.179                                                   & 2.694                                                 & 3.565                                                      \\ \hline
Triangle                & 1.531                                                   & 1.493                                                      & 1.563                                                      \\ \hline
MQ Score                & 0.041                                                   & 0.018                                                      & 0.063                                                      \\ \hline
Same Issue Area         & 1.061                                                   & 1.028                                                      & 1.099                                                      \\ \hline
Year Difference         & 0.010                                                   & 0.008                                                     & 0.013                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period 1937-2001}
\label{bootMPLE_total}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.391                                                 & -5.506                                                     & -5.244                                                     \\ \hline
Instar(2)               & 0.035                                                   & 0.028                                                      & 0.042                                                      \\ \hline
Outstar(2)              & 0.015                                                   & 0.0003                                                      & 0.017                                                      \\ \hline
Mutual                  & 4.785                                                   & 3.616                                                 & 5.749                                                      \\ \hline
Triangle                & 1.377                                                   & 1.271                                                      & 1.513                                                      \\ \hline
MQ Score                & -0.018                                                   & -0.095                                                      & 0.061                                                      \\ \hline
Same Issue Area         & 1.229                                                   & 1.126                                                      & 1.327                                                      \\ \hline
Year Difference         & -0.077                                                   & -0.096                                                     & -0.061                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Fred M. Vinson was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.032                                                 & -5.140                                                     & -4.931                                                     \\ \hline
Instar(2)               & 0.028                                                   & 0.025                                                      & 0.032                                                      \\ \hline
Outstar(2)              & 0.018                                                   & 0.015                                                      & 0.022                                                      \\ \hline
Mutual                  & 3.166                                                   & 1.826                                                 & 4.565                                                      \\ \hline
Triangle                & 1.520                                                   & 1.449                                                      & 1.599                                                      \\ \hline
MQ Score                & -0.101                                                   & -0.149                                                      & -0.052                                                      \\ \hline
Same Issue Area         & 1.349                                                   & 1.289                                                      & 1.408                                                      \\ \hline
Year Difference         & -0.031                                                   & -0.038                                                     & -0.026                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Earl Warren was chief justice.}
\label{bootMPLE_warren}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.952                                                 & -4.017                                                     & -3.882                                                     \\ \hline
Instar(2)               & 0.015                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.004                                                   & 0.002                                                      & 0.006                                                      \\ \hline
Mutual                  & 2.558                                                   & 1.425                                                 & 3.719                                                      \\ \hline
Triangle                & 1.383                                                   & 1.333                                                      & 1.440                                                      \\ \hline
MQ Score                & -0.084                                                   & -0.101                                                      & -0.059                                                      \\ \hline
Same Issue Area         & 0.959                                                   & 0.911                                                      & 1.008                                                      \\ \hline
Year Difference         & -0.017                                                   & -0.019                                                     & -0.015                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Warren E. Burger was chief justice.}
\label{bootMPLE_burger}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.614                                                 & -3.701                                                     & -3.525                                                     \\ \hline
Instar(2)               & 0.015                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.002                                                   & -0.002                                                      & 0.004                                                      \\ \hline
Mutual                  & 9.635                                                  & 6.426                                                 & 10.834                                                      \\ \hline
Triangle                & 1.551                                                   & 1.489                                                      & 1.620                                                      \\ \hline
MQ Score                & -0.007                                                   & -0.039                                                      & 0.028                                                      \\ \hline
Same Issue Area         & 0.855                                                   & 0.794                                                      & 0.916                                                      \\ \hline
Year Difference         & -0.016                                                   & -0.018                                                     & -0.014                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when William Rehnquist was chief justice.}
\label{bootMPLE_rehnquist}
\end{table}

>>>>

\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|} 
\hline
                                                   & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound & \cellcolor[HTML]{EFEFEF}Significance \\
                                                    \hline
Edges                                              & -5.533                           & -5.733                              & -5.388                              & *                                    \\ \hline
Instar(2)                                          & 0.031                            & 0.027                               & 0.036                               & *                                    \\ \hline
Outstar(2)                                         & 0.022                            & 0.020                               & 0.032                               & *                                    \\ \hline
Mutual                                             & 3.316                            & 2.622                               & 3.983                               & *                                    \\ \hline
Triangle                                           & 1.490                            & 1.410                               & 1.560                               & *                                    \\ \hline
Martin Quinn Score                                 & 0.080                            & 0.022                               & 0.126                               & *                                    \\ \hline
Same Issue Area Homophily                          & 1.378                            & 1.313                               & 1.451                               & *                                    \\ \hline
Year Difference                                    & -0.077                           & -0.090                              & -0.064                              & *                                    \\ \hline
$(\text{Year Differnce})^2$                        & 0.0029                           & 0.0025                              & 0.0032                              & *                                    \\ \hline
Receiver Abs Diff MQ Score in Majority             & -0.030                           & -0.048                              & -0.014                              & *                                    \\ \hline
Receiver Number Justices in Majority               & -0.115                           & -0.135                              & -0.089                              & *                                    \\ \hline
Receiver  Sender Year                              & 0.0007                           & 0.0006                              & 0.0009                              & *                                    \\ \hline
Sender Same Issue Area 2                           & 0.162                            & 0.105                               & 0.217                               & *                                    \\ \hline
Sender Same Issue Area 3                           & -0.317                           & -0.403                              & -0.236                              & *                                    \\ \hline
Sender Same Issue Area 4                           & 0.497                            & 0.426                               & 0.570                               & *                                    \\ \hline
Sender Same Issue Area 5                           & 0.332                            & 0.174                               & 0.495                               & *                                    \\ \hline
Sender Same Issue Area 6                           & 0.527                            & 0.402                               & 0.635                               & *                                    \\ \hline
Sender Same Issue Area 7                           & 0.327                            & 0.251                               & 0.394                               & *                                    \\ \hline
Sender Same Issue Area 8                           & 0.076                            & 0.021                               & 0.129                               & *                                    \\ \hline
Sender Same Issue Area 9                           & 0.261                            & 0.209                               & 0.315                               & *                                    \\ \hline
Sender Same Issue Area 10                          & 0.369                            & 0.301                               & 0.432                               & *                                    \\ \hline
Sender Same Issue Area 11                          & -0.046                           & -0.233                              & 0.151                               &                                      \\ \hline
Sender Same Issue Area 12                          & 0.0073                           & -0.075                              & 0.089                               &                                      \\ \hline
Sender Same Issue Area 13                          & 0.381                            & 0.162                               & 0.564                               & *                                    \\ \hline
Sender Same Issue Area 14                          & 0.151                            & -0.019                              & 0.300                               &                                      \\ \hline
Receiver Same Issue Area 2                         & 0.231                            & 0.166                               & 0.300                               & *                                    \\ \hline
Receiver Same Issue Area 3                         & -0.101                           & -0.209                              & -0.006                              & *                                    \\ \hline
Receiver Same Issue Area 4                         & 0.516                            & 0.425                               & 0.612                               & *                                    \\ \hline
Receiver Same Issue Area 5                         & 0.351                            & 0.183                               & 0.534                               & *                                    \\ \hline
Receiver Same Issue Area 6                         & 0.461                            & 0.284                               & 0.628                               & *                                    \\ \hline
Receiver Same Issue Area 7                         & 0.361                            & 0.281                               & 0.437                               & *                                    \\ \hline
Receiver Same Issue Area 8                         & 0.153                            & 0.097                               & 0.221                               & *                                    \\ \hline
Receiver Same Issue Area 9                         & 0.279                            & 0.221                               & 0.346                               & *                                    \\ \hline
Receiver Same Issue Area 10                        & 0.492                            & 0.413                               & 0.570                               & *                                    \\ \hline
Receiver Same Issue Area 11                        & 0.247                            & 0.056                               & 0.411                               & *                                    \\ \hline
Receiver Same Issue Area 12                        & 0.339                            & 0.246                               & 0.430                               & *                                    \\ \hline
Receiver Same Issue Area 13                        & 1.060                            & 0.845                               & 1.239                               & *                                    \\ \hline
Receiver Same Issue Area 14                        & 0.557                            & 0.255                               & 0.793                               & *                                    \\ \hline
Instar(2) $\times$ Sender Year                     & -0.00025                         & -0.00034                            & -0.00017                            & *                                    \\ \hline
Outstar(2) $\times$ Sender Year                    & -0.00036                         & -0.00056                            & -0.00028                            & *                                    \\ \hline
Mutual $\times$ Sender Year                        & -0.010                           & -0.043                              & 0.029                               &                                      \\ \hline
Triangle $\times$ Sender Year                      & -0.0004                          & -0.0021                             & 0.0016                              &                                      \\ \hline
Martin Quinn Score $\times$ Sender Year            & -0.0025                          & -0.0035                             & -0.0013                             & *                                    \\ \hline
Same Issue Area $\times$ Sender Year               & -0.0058                          & -0.0076                             & -0.0043                             & *                                    \\ \hline
Year Difference $\times$ Sender Year               & 0.0004                           & 0.0002                              & 0.0007                              & *                                    \\ \hline
$\text{Year Difference}^2 \times$ Sender Year      & -0.000037                        & -0.000044                           & -0.000030                           & *                                    \\ \hline
MQ Score in Majority $\times$ Sender Year & 0.0013                           & 0.0009                              & 0.0017                              & *                                    \\ \hline
Justices in Majority $\times$ Sender Year   & 0.0029                           & 0.0023                              & 0.0035                              & *                                    \\ \hline
\end{tabular}
\caption{Bootstrapped MPLE Results for the time period $1937-2001$. A '*' indicates that the 2.5th and 97.5th quantile of the variable does not include '0' and as a result is statistically significant.}
\label{my-label}
\end{table}
